ComBatLS LBCC Results

### 2025-01-31 eda/lifespan_eda.Rmd
updates

```{r}
fig5_AB <- ggarrange(fig5A, full_rain,
          nrow=1, ncol=2, 
          #legend = "none",
          widths=c(1.8, 1),
          labels = "AUTO")
fig5_AB
#saveRDS(fig5_AB, file="../figs/figure_5_AB.rds")
ggsave("../figs/fig5_ab.jpeg", fig5_AB, width=18, height=10, units="in")
```

>>>>

```{r}
fig5_AB <- ggarrange(fig5A, full_rain,
          nrow=1, ncol=2, 
          #legend = "none",
          widths=c(1.8, 1),
          labels = "AUTO")
fig5_AB
saveRDS(fig5_AB, file="../figs/figure_5_AB.rds")
ggsave("../figs/fig5_ab.jpeg", fig5_AB, width=18, height=10, units="in")
```

### 2025-01-31 paper_lbcc_results.Rmd
updates

@@

```{r}
gam_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-log-cf-cf.gam-batch.study_predictions.csv"))

gam_centile_df <- left_join(gam_centile_df, study_site_key) %>% 
  mutate(age_years=(age_days-280)/365.25)
n_unique(gam_centile_df$study)

dim(gam_centile_df)

gam_centile_df %>% dplyr::filter(is.na(age_days))
```

Combat-LS Centiles
```{r}
gamlss_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-log-cf-cf.gamlss-batch.study_predictions.csv"))
gamlss_centile_df <- full_join(gamlss_centile_df, study_site_key) %>% 
    mutate(age_years=(age_days-280)/365.25)

@@

Unharmonized Centiles
```{r}
raw_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-raw_predictions.csv"))
raw_centile_df <- full_join(raw_centile_df, study_site_key) %>% 
    mutate(age_years=(age_days-280)/365.25)

@@

```{r}
deltas_df <- fread(file=paste0(der_path, "/batch.study_pred_deltas.csv"))
deltas_df <- full_join(deltas_df, study_site_key) %>% 
    mutate(age_years=(age_days-280)/365.25)

@@

```{r}
raw_centile_df.mean <- raw_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_cent=mean(centile))
nrow(raw_centile_df.mean) == n_unique(raw_centile_df.mean$participant)
```

@@

```{r}
raw_z_df.mean <- raw_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(raw_z_df.mean) == n_unique(raw_z_df.clean$participant)
```

@@

```{r}
gam_centile_df.mean <- gam_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_cent=mean(centile))
nrow(gam_centile_df.mean) == n_unique(gam_centile_df.mean$participant)
```

@@

```{r}
gam_z_df.mean <- gam_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(gam_z_df.mean) == n_unique(gam_z_df.clean$participant)
```

@@

```{r}
gamlss_centile_df.mean <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            log_age=unique(log_age),
            sexMale=unique(sexMale),
            fs_version=unique(fs_version),
            mean_cent=mean(centile))
nrow(gamlss_centile_df.mean) == n_unique(gamlss_centile_df.mean$participant)
```

@@

```{r}
gamlss_z_df.mean <- gamlss_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site=unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(gamlss_z_df.mean) == n_unique(gamlss_z_df.clean$participant)
```

@@

f2.df %>%
  group_by(combat) %>%
  summarize(median = median(fsq),
            IQR = IQR(fsq))
```

@@

```{r}
f2.df.sum <- f2.df %>%
  dplyr::filter(combat != "Umharmonized") %>%
  group_by(pheno) %>%
  arrange(combat) %>%
  mutate(F2_diff = fsq - fsq[1]) #gamlss - gam value, + number means site effect is larger in combatLS

@@

Get study info
```{r}
study_info <- raw_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(study) %>%
  summarize(study_mean_age=mean(age_years),
            study_median_age=median(age_years),
            study_n= n()) %>%
  dplyr::select(study, study_mean_age, study_median_age, study_n)
```

@@

#get subject-level means
mean_cent_deltas_df <- cent_deltas_df %>%
  pivot_longer(cols=any_of(paste0("delta.", pheno_list)), names_to="pheno", values_to = "centile") %>%
  group_by(participant) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_delta_cent=(mean(centile))*100, #convert units to centiles space
            abs_mean_delta_cent=(mean(abs(centile)))*100)

mean_cent_deltas_df_study <- full_join(mean_cent_deltas_df, study_info)

@@

see how often features move between extreme (>95% or <5%) to not-extreme
```{r}
#rm features that didn't converge in both datasets
pheno_list_cent <- pheno_list[pheno_list != "lh_SA_posteriorcingulate" & pheno_list != "rh_CT_posteriorcingulate"]

gam_centile_df.clean$combat <- "cf.gam"
gamlss_centile_df.clean$combat <- "cf.gamlss"

@@

centiles_cat <- centiles_df %>%
  mutate(combat = factor(combat, ordered=TRUE, levels=c("cf.gam", "cf.gamlss"))) %>%
  mutate(across(pheno_list_cent, ~ as.factor(case_when(. > 0.95 ~ "high", 
                                               . < 0.05 ~ "low",
                                               TRUE ~ "mid")))) %>%
  arrange(combat) %>%
  group_by(participant) %>%
  mutate(across(pheno_list_cent, 
                ~ . == first(.), .names = "is_equal_{col}")) %>%
  ungroup()
```

```{r}
centiles_cat_filt <- centiles_cat %>%
  dplyr::select(participant, combat, all_of(pheno_list_cent))

ext_count_df <- centiles_cat_filt %>%
  rowwise() %>%
  mutate(count_high = sum(c_across(pheno_list_cent) == "high"),
         count_mid = sum(c_across(pheno_list_cent) == "mid"),
         count_low = sum(c_across(pheno_list_cent) == "low")) %>%
  dplyr::select(participant, combat, starts_with("count"))

@@

```{r}
centiles_cat_filt2 <- centiles_cat %>%
  dplyr::filter(combat =="cf.gamlss") %>%
  dplyr::select(participant, starts_with("is_equal_")) %>%
  mutate(sum = rowSums(across(starts_with("is_equal_")))) %>%
  mutate(changed = ifelse(sum == length(pheno_list_cent), "no_change", "change")) #if not all features are true -> changed

max(centiles_cat_filt2$sum) == length(pheno_list_cent) #correct

length(pheno_list_cent) - mean(centiles_cat_filt2$sum) #mean per subject
length(pheno_list_cent) - min(centiles_cat_filt2$sum) #range
length(pheno_list_cent) - max(centiles_cat_filt2$sum)

@@

#percentage features
#n changed features = # total features - sum
n_feat <- n_unique(centiles_cat_filt2$participant)*length(pheno_list_cent)
n_unchanged <- sum(centiles_cat_filt2$sum) #true = 1 = no change

@@

n_unique(centiles_cat_filt2_long$participant)*206 == nrow(centiles_cat_filt2_long)

@@

@@

```{r}
# study demographics
fig5_vert <- ggarrange(
  #ggarrange(blank,
ggarrange(sample_boxplot2, full_boxplot2,
          sample_barplot2, full_barplot2,
          nrow=2, ncol=2, 
          #align = "v", 
          common.legend = TRUE,
          legend = "right",
          widths=c(18, 1),
          heights=c(1, 1)
          ),
# blank,
# nrow=1, ncol=3,
# common.legend = FALSE,
# widths= c(1, 20, 1)),
# boxplots
mean_cents_bxplt_nolabel,
common.legend=FALSE,
nrow=2, ncol=1,
heights=c(1, 1.5),
labels="AUTO"
)

ggsave("figs/figure_5_vertical.jpeg", fig5_vert, width=15, height=9, units="in")
```

@@

#predict w CIs
pdat <- with(mean_cent_deltas_df_study,
             tibble(study_mean_age = seq(min(study_mean_age),
                            max(study_mean_age),
                            length = 200),
             study_n = rep(median(study_n), length=200)))

pred_abs_lm <- predict(abs_lm, pdat, se.fit=TRUE)

pred_df <- pdat %>% 
  bind_cols(data.frame(pred_abs_lm))

pred_df <- pred_df %>%
  mutate(upper = fit + (1.96 * se.fit), #95% CIs
         lower = fit - (1.96 * se.fit))

mean_delta_fig <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = study_mean_age), data = pred_df,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df, aes(y = fit, x=study_mean_age))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Mean Age of Primary Study Sample (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
ggsave("figs/supp_mean_delta_fig.jpeg", mean_delta_fig, width=10, height=7, units="in")
```

@@

Cornell_C2 has very low n=5 -> big differences in estimation

@@

#predict w CIs
pdat2 <- with(mean_cent_deltas_df_study,
             tibble(abs_age_diff = seq(min(abs_age_diff),
                            max(abs_age_diff),
                            length = 200),
             study_n = rep(median(study_n), length=200),
             study_mean_age = rep(median(study_mean_age), length=200)))

pred2 <- predict(abs_lm2, pdat2, se.fit = TRUE)

pdat2 <- pdat2 %>%
  bind_cols(data.frame(pred2)) %>%
  mutate(upper = fit + (1.96 * se.fit),
         lower = fit - (1.96 * se.fit))

mean_delta_fig2 <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=abs_age_diff, y=abs_mean_delta_cent)) +
  geom_point(alpha=0.05, aes(color=study)) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = abs_age_diff), data = pdat2,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pdat2, aes(y = fit, x=abs_age_diff)) +
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Subject's Offset from Mean Age of Primary Study (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
ggsave("figs/supp_mean_delta_fig2.jpeg", mean_delta_fig2, width=10, height=7, units="in")
```

>>>>

Requires the following inputs from cluster:

 - `lifespan-CN-imp-sites-euler-log-cf-cf.gam-batch.study_predictions.csv`
 - `lifespan-CN-imp-sites-euler-log-cf-cf.gamlss-batch.study_predictions.csv`
 - `lifespan-CN-imp-sites-euler-raw_predictions.csv`
 - `batch.study_pred_deltas.csv`
 - `lifespan-CN-imp-sites-euler-raw_cohenfsq.csv`
 - `lifespan-CN-imp-sites-euler-log-cf-cf.gam-batch.study-data_cohenfsq.csv`
 - `lifespan-CN-imp-sites-euler-log-cf-cf.gamlss-batch.study-data_cohenfsq.csv`

@@

```{r}
gam_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-log-cf-cf.gam-batch.study-data_no.tbv_predictions.csv"))

gam_centile_df <- left_join(gam_centile_df, study_site_key) %>% 
  mutate(age_years=(age_days-280)/365.25) %>%
  unite(INDEX.ID, c(study, participant, sex), sep = "|", remove=FALSE)
n_unique(gam_centile_df$study)

dim(gam_centile_df)
```

Combat-LS Centiles
```{r}
gamlss_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-log-cf-cf.gamlss-batch.study-data_no.tbv_predictions.csv"))
gamlss_centile_df <- full_join(gamlss_centile_df, study_site_key) %>% 
  mutate(age_years=(age_days-280)/365.25) %>%
  unite(INDEX.ID, c(study, participant, sex), sep = "|", remove=FALSE)

@@

Unharmonized Centiles
```{r}
raw_centile_df <- fread(file=paste0(der_path, "/lifespan-CN-imp-sites-euler-raw_no.tbv_predictions.csv"))
raw_centile_df <- full_join(raw_centile_df, study_site_key) %>%
  unite(INDEX.ID, c(study, participant, sex), sep = "|", remove=FALSE) %>%
  mutate(age_years=(age_days-280)/365.25)

@@

```{r}
deltas_df <- fread(file=paste0(der_path, "/batch.study-data_no.tbv_predictions_pred_deltas.csv"))
deltas_df <- full_join(deltas_df, study_site_key) %>% 
  unite(INDEX.ID, c(study, participant, sex), sep = "|", remove=FALSE) %>%
  mutate(age_years=(age_days-280)/365.25)

@@

```{r}
raw_centile_df.mean <- raw_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_cent=mean(centile))
nrow(raw_centile_df.mean) == n_unique(raw_centile_df.mean$INDEX.ID)
```

@@

```{r}
raw_z_df.mean <- raw_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(raw_z_df.mean) == n_unique(raw_z_df.clean$INDEX.ID)
```

@@

```{r}
gam_centile_df.mean <- gam_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_cent=mean(centile))
nrow(gam_centile_df.mean) == n_unique(gam_centile_df.mean$INDEX.ID)
```

@@

```{r}
gam_z_df.mean <- gam_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(gam_z_df.mean) == n_unique(gam_z_df.clean$INDEX.ID)
```

@@

```{r}
gamlss_centile_df.mean <- gamlss_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            log_age=unique(log_age),
            sexMale=unique(sexMale),
            fs_version=unique(fs_version),
            mean_cent=mean(centile))
nrow(gamlss_centile_df.mean) == n_unique(gamlss_centile_df.mean$INDEX.ID)
```

@@

```{r}
gamlss_z_df.mean <- gamlss_z_df.clean %>%
  pivot_longer(cols=any_of(pheno_list.z), names_to="pheno", values_to = "z_score") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site=unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_z=mean(z_score))
nrow(gamlss_z_df.mean) == n_unique(gamlss_z_df.clean$INDEX.ID)
```

@@

f2.df %>%
  group_by(combat) %>%
  summarize(median = median(fsq),
            IQR = IQR(fsq))

length(unique(f2.df$pheno))
setdiff(pheno_list, unique(f2.df$pheno)) #pheno not loaded
```

@@

```{r}
f2.df.sum <- f2.df %>%
  dplyr::filter(combat != "Unharmonized") %>%
  group_by(pheno) %>%
  arrange(combat) %>%
  mutate(F2_diff = fsq - fsq[1]) #gamlss - gam value, + number means site effect is larger in combatLS

@@

Get study info
```{r}
study_info <- raw_centile_df.clean %>%
  pivot_longer(cols=any_of(pheno_list), names_to="pheno", values_to = "centile") %>%
  group_by(study) %>%
  summarize(study_mean_age=mean(age_years),
            study_median_age=median(age_years),
            study_n= n(),
            age_range = max(age_years) - min(age_years)) %>%
  dplyr::select(study, study_mean_age, study_median_age, study_n, age_range)
```

@@

#get subject-level means
mean_cent_deltas_df <- cent_deltas_df %>%
  pivot_longer(cols=any_of(paste0("delta.", pheno_list)), names_to="pheno", values_to = "centile") %>%
  group_by(INDEX.ID) %>%
  summarize(study = unique(study),
            site = unique(site),
            age_days=unique(age_days),
            sex=unique(sex),
            mean_delta_cent=(mean(centile))*100, #convert units to centiles space
            abs_mean_delta_cent=(mean(abs(centile)))*100)

mean_cent_deltas_df_study <- full_join(mean_cent_deltas_df, study_info)
mean_cent_deltas_df_study <- mean_cent_deltas_df_study %>%
  mutate(age_diff = (age_days/365.25) - study_mean_age,
         abs_age_diff = abs(age_diff))

@@

see how often features move between extreme (>95% or <5%) to not-extreme
```{r}
gam_centile_df.clean$combat <- "cf.gam"
gamlss_centile_df.clean$combat <- "cf.gamlss"

@@

centiles_cat <- centiles_df %>%
  mutate(combat = factor(combat, ordered=TRUE, levels=c("cf.gam", "cf.gamlss"))) %>%
  mutate(across(pheno_list, ~ as.factor(case_when(. > 0.95 ~ "high", 
                                               . < 0.05 ~ "low",
                                               TRUE ~ "mid")))) %>%
  arrange(combat) %>%
  group_by(INDEX.ID) %>%
  mutate(across(pheno_list, 
                ~ . == first(.), .names = "is_equal_{col}")) %>%
  ungroup()
saveRDS(centiles_cat, file="centiles_cat.rds")
```

```{r}
centiles_cat_filt <- centiles_cat %>%
  dplyr::select(INDEX.ID, combat, all_of(pheno_list))

ext_count_df <- centiles_cat_filt %>%
  rowwise() %>%
  mutate(count_high = sum(c_across(pheno_list) == "high"),
         count_mid = sum(c_across(pheno_list) == "mid"),
         count_low = sum(c_across(pheno_list) == "low")) %>%
  dplyr::select(INDEX.ID, combat, starts_with("count"))

@@

```{r}
centiles_cat_filt2 <- centiles_cat %>%
  dplyr::filter(combat =="cf.gamlss") %>%
  dplyr::select(INDEX.ID, starts_with("is_equal_")) %>%
  mutate(sum = rowSums(across(starts_with("is_equal_")))) %>%
  mutate(changed = ifelse(sum == length(pheno_list), "no_change", "change")) #if not all features are true -> changed

stopifnot(max(centiles_cat_filt2$sum) == length(pheno_list)) #correct

length(pheno_list) - mean(centiles_cat_filt2$sum) #mean per subject
length(pheno_list) - min(centiles_cat_filt2$sum) #range
length(pheno_list) - max(centiles_cat_filt2$sum)

@@

#percentage features
#n changed features = # total features - sum
n_feat <- n_unique(centiles_cat_filt2$INDEX.ID)*length(pheno_list)
n_unchanged <- sum(centiles_cat_filt2$sum) #true = 1 = no change

@@

n_unique(centiles_cat_filt2_long$INDEX.ID)*208 == nrow(centiles_cat_filt2_long)

@@

similarly, studies with larger age ranges change more
```{r}
summary(lm(abs_mean_delta_cent ~ age_range + study_n, data=mean_cent_deltas_df_study))

mean_cent_deltas_df_study %>%
  ggplot(aes(x=age_range, y=abs_mean_delta_cent, color=study)) +
  geom_point(alpha=0.05) +
  geom_smooth(method="lm") +
  theme(legend.position = "none")
```

@@

```{r}
demo_plt <- readRDS("figs/figure_5_AB.rds")

# study demographics
fig5_vert <- ggarrange(
#   #ggarrange(blank,
# ggarrange(sample_boxplot2, full_boxplot2,
#           sample_barplot2, full_barplot2,
#           nrow=2, ncol=2, 
#           #align = "v", 
#           common.legend = TRUE,
#           legend = "right",
#           widths=c(18, 1),
#           heights=c(1, 1)
#           ),
# blank,
# nrow=1, ncol=3,
# common.legend = FALSE,
# widths= c(1, 20, 1)),
# boxplots
demo_plt,
mean_cents_bxplt_nolabel,
common.legend=FALSE,
nrow=2, ncol=1,
heights=c(2, 1),
labels=c("", "C")
)

ggsave("figs/figure_5_vertical.jpeg", fig5_vert, width=17, height=15, units="in")
```

@@

#predict w CIs
pdat1 <- with(mean_cent_deltas_df_study,
             tibble(study_mean_age = seq(min(study_mean_age),
                            max(study_mean_age),
                            length = 200),
             study_n = rep(median(study_n), length=200)))

pred_abs_lm1 <- predict(abs_lm, pdat1, se.fit=TRUE)

pred_df1 <- pdat1 %>% 
  bind_cols(data.frame(pred_abs_lm1))

pred_df1 <- pred_df1 %>%
  mutate(upper = fit + (1.96 * se.fit), #95% CIs
         lower = fit - (1.96 * se.fit))

mean_delta_fig <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = study_mean_age), data = pred_df1,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df1, aes(y = fit, x=study_mean_age))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Mean Age of Primary Study Sample (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
#ggsave("figs/supp_mean_delta_fig.jpeg", mean_delta_fig, width=10, height=7, units="in")
```

mean abs delta ~ study range

```{r}
range_mod <- lm(abs_mean_delta_cent ~ age_range + study_n, data=mean_cent_deltas_df_study)
summary(range_mod)

#predict w CIs
pdat2 <- with(mean_cent_deltas_df_study,
             tibble(age_range = seq(min(age_range),
                            max(age_range),
                            length = 200),
             study_n = rep(median(study_n), length=200)))

pred_abs_lm2 <- predict(range_mod, pdat2, se.fit=TRUE)

pred_df2 <- pdat2 %>% 
  bind_cols(data.frame(pred_abs_lm2))

pred_df2 <- pred_df2 %>%
  mutate(upper = fit + (1.96 * se.fit), #95% CIs
         lower = fit - (1.96 * se.fit))

range_delta_fig <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=age_range, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = age_range), data = pred_df2,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df2, aes(y = fit, x=age_range))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Age Range of Primary Study Sample (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
```

@@

@@

#predict w CIs
pdat3 <- with(mean_cent_deltas_df_study,
             tibble(abs_age_diff = seq(min(abs_age_diff),
                            max(abs_age_diff),
                            length = 200),
             study_n = rep(median(study_n), length=200),
             study_mean_age = rep(median(study_mean_age), length=200)))

pred3 <- predict(abs_lm2, pdat3, se.fit = TRUE)

pdat3 <- pdat3 %>%
  bind_cols(data.frame(pred3)) %>%
  mutate(upper = fit + (1.96 * se.fit),
         lower = fit - (1.96 * se.fit))

mean_delta_fig2 <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=abs_age_diff, y=abs_mean_delta_cent)) +
  geom_point(alpha=0.05, aes(color=study)) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = abs_age_diff), data = pdat3,
                inherit.aes = FALSE, alpha = 0.4) +
    geom_line(data = pdat3, aes(y = fit, x=abs_age_diff)) +
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Subject's Offset from Mean Age of Primary Study (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
#ggsave("figs/supp_mean_delta_fig2.jpeg", mean_delta_fig2, width=10, height=7, units="in")
```
